% Based on template: http://www.maths.lth.se/matematiklth/exjobb/exjobbarresurs/index.html

\documentclass[a4paper]{article}

\usepackage[smartEllipses]{markdown}  % For markdown
\def\markdownOptionOutputDir{build}  % Needed, see https://github.com/Witiko/markdown/issues/6#issuecomment-328699108

\usepackage[dvipsnames]{xcolor}
\usepackage{hyperref}
\usepackage{comment}
\usepackage{xargs}
\usepackage{verbatim}
\usepackage[colorinlistoftodos, prependcaption, textsize=tiny]{todonotes}

\usepackage[english]{datetime2}
\DTMnewdatestyle{dashdate}{%
  \renewcommand{\DTMdisplaydate}[4]{\number##1-\DTMenglishshortmonthname{##2}-\number##3}%
  \renewcommand{\DTMDisplaydate}{\DTMdisplaydate}%
}
\DTMsetdatestyle{iso}

% From: https://tex.stackexchange.com/a/178806/36302
\newcommandx{\add}[2][1=]{\todo[linecolor=red, backgroundcolor=red!25, bordercolor=red, inline, #1]{\textbf{Add:} #2}}
\newcommandx{\unsure}[2][1=]{\todo[linecolor=red, backgroundcolor=red!25, bordercolor=red, #1]{\textbf{Unsure:} #2}}
\newcommandx{\change}[2][1=]{\todo[linecolor=blue, backgroundcolor=blue!25, bordercolor=blue, #1]{\textbf{Change:} #2}}
\newcommandx{\info}[2][1=]{\todo[linecolor=OliveGreen, backgroundcolor=OliveGreen!25, bordercolor=OliveGreen, #1]{\textbf{Info:} #2}}
\newcommandx{\improvement}[2][1=]{\todo[linecolor=Plum, backgroundcolor=Plum!25,bordercolor=Plum, #1]{\textbf{Improve:} #2}}
\newcommandx{\thiswillnotshow}[2][1=]{\todo[disable, #1]{#2}}

% Formatting
\setlength{\parindent}{0pt}
\setlength{\parskip}{1em}

% Encoding and languages
\usepackage[T1]{fontenc}        % För svenska bokstäver
%\usepackage[swedish]{babel}    %Svenska skrivregler och rubriker

% Graphics
\usepackage{epsfig}
%\usepackage[dvips]{graphics}

\newcommand\myshade{85}
\colorlet{mylinkcolor}{violet}
\colorlet{mycitecolor}{YellowOrange}
\colorlet{myurlcolor}{Aquamarine}

\hypersetup{%
  linkcolor  = black, %mylinkcolor!\myshade!black,
  citecolor  = mycitecolor!\myshade!black,
  urlcolor = myurlcolor!\myshade!black,
  colorlinks = true,
}

% References
\usepackage[backend=biber, style=numeric, sorting=none]{biblatex}
\usepackage{cleveref}
\bibliography{zotero}
\DeclareBibliographyCategory{cited}
\AtEveryCitekey{\addtocategory{cited}{\thefield{entrykey}}}

\defbibheading{notcited}{\section*{Further Reading}}

\title{%
    \small DRAFT \today \\
    \small The latest version is available at \href{https://erik.bjareholt.com/thesis/thesis.pdf}{erik.bjareholt.com/thesis/thesis.pdf}\\
    \large --- \\
    \large \par M.Sc. Thesis\\
    \huge Classifying brain activity using low-cost biosensors and automated time tracking \\
}
\author{Erik Bjäreholt \\(erik@bjareho.lt, dat13ebj@student.lu.se)}
\date{\today}

\begin{document}
\maketitle

\begin{abstract}
Här skriver jag in mitt abstract.
\end{abstract}

\pagebreak.\pagebreak

\tableofcontents

\listoftodos[Notes \& TODOs]

\pagebreak.\pagebreak

\section{Introduction}

Testing.

\subsection{Background}

\add{Insert stuff from goal document}

\subsection{Aim of the thesis}

\add{Insert stuff from goal document}

\subsection{Related work}

\add{Insert stuff from Fucci et al.}

\section{Methods}

\section{Results}

\section{Conclusions}

\section*{Acknowledgements}

\begin{markdown}
 - My advisor

 - The NeuroTechX crowd

 - My brother Johan Bjäreholt, for working with me on ActivityWatch all these years.
\end{markdown}

The Oxford English Dictionary defines `thesis' as `a long essay or dissertation involving personal research, written by a candidate for a university degree.', and I can't think of more personal research than research in quantified self with personal data.

\end{document}
